Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-23 paper.tex
Updated figures

In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{StormCutoff}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\section{Appendix}
\subsection{Bias}
While attempting to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found. It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, and whether the hourly medians are an hour ahead of each hour grid point, or a median of points a half hour to either side, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias. These attempts are shown in Figure \ref{blockmedian}. This also shows the effect of only considering events with a minimum before noon. All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}. Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$. Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.

@@

\section{Figures}

\begin{figure}[htp]
\centering
\includegraphics[scale=0.7]{paperfigures/alldata.eps}
\caption{Overview of data used in this study. The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text. Dashed lines indicate default event cutoff thresholds.}
\label{AllData}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\caption{(a) One-day medians of $D_{st}$ storms at a threshold of $-40nT$ and (b) verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991}
\label{DailyAverages}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
\caption{(a) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (b) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. (c) All data of $D_{st}$ and $\rho_{eq}$ }
\label{ccplot}
\end{figure}
\clearpage

% Change x-label to be ``Time from start of event (hr)'' and put vertical lines in each panel at t = 0 (somewhere I have a code called vertline.m)
\begin{figure}[htp]
\centering
(a)
\includegraphics[scale=0.7]{paperfigures/massdensitystorms.eps}
(b)
\includegraphics[scale=0.7]{paperfigures/dststorms.eps}
\caption{Averages around time of (a) 669 $\rho_{eq}$ and (b) 130 $D_{st}$ events along with thresholds used to define an event. The number of values used in the averages for mass density is shown in the bottom panel (a) and (b).}
\label{StormCutoff}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
\caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
\label{Mspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
\label{Dspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-10amu.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-diffden-30percent.eps}
\caption{diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$, diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
\label{rhochange}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-nof107.eps}
\includegraphics[scale=0.6]{paperfigures/f107removed.eps}
\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
\label{nof107}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated storms. (b) Same, but only storms starting between 0-12 UTC}
\label{blockmedian}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.9]{paperfigures/allstorms.eps}
\caption{Comparing all storms to their median and $1\sigma$ range}
\label{allstorms}
\end{figure}
\clearpage

>>>>

In this work events are considered when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in \ref{AllData}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_Z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\section{Appendix}
\subsection{Bias}
While attempting to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found. It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, and whether the hourly medians are an hour ahead of each hour grid point, or a median of points a half hour to either side, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias. These attempts are shown in Figure \ref{blockmedian}. This also shows the effect of only considering events with a minimum before noon. All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}. Figure \ref{allstorms} shows where the median falls for all of the found events during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$. Both authors of this paper conducted independent trials to confirm that the data and analysis don't quite yield the results of Figure 11 in \cite{Takahashi2010} with the processes described in that paper, but the same general trend is still seen.

@@

\clearpage
\section{Figures}

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata.eps}
\caption{Overview of data used in this study. The top four panels are from \cite{Reconstruction} and the bottom panel is based on \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines indicate default event cutoff thresholds.}
\label{AllData}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
\label{ccplot}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) One-day medians of $D_{st}$ events at a threshold of $-40nT$}
\label{DailyAverages}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50~nT$ onset. (b) Same as (a) except around time intervals where mass density crossed above $40~amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50~nT$ for at least 12~hours. (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50~amu/cm^3$ for at least 12 hours.}
\label{Mspec}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80nT$ (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
\label{Dspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
\label{rhochange}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
\includegraphics[scale=0.5]{paperfigures/f107removed.eps}
\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
\label{nof107}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events. (b) Same, but only events starting between 0-12 UTC}
\label{blockmedian}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.9]{paperfigures/allstorms.eps}
\caption{Comparing all events to their median and $1\sigma$ range}
\label{allstorms}
\end{figure}
\clearpage
